An Introduction to Rocker:\\ Docker Containers for R

### 2017-11-24 boettiger-eddelbuettel.Rmd
three small changes based on proofreading-checklist

### Community Optimized

Having a shared, transparent computational environment created by a publicly hosted, reproducible
recipe facilitates community input into configuration details. R and many of its packages
and related software can be configured with a wide range of options, compilers, different
linear-algebra libraries and so forth.  While this flexibility reflects varying needs,
many users rely on default settings which are most often are optimized more for 
simplicity of installation rather than than performance.
The Rocker recipes reflect significant community input on these choices.
This helps create a more finely tuned, optimized reference
implementation of the R environment as well as a platform for comparing and discussing these 
concerns which are often overlooked elsewhere.  Issues and Pull Requests on the Rocker 
repositories on GitHub attest to some of these discussions and improvements.
In particular, input from the Docker Inc employees through the official approval process
for the `r-base` image, expertise from the Debian R maintainer and other Debian developers,
and both direct and indirect feedback from the experience and user-generated documentation
from many early adopters in the R community has helped shape and strengthen the project
over the past few years.
Widespread use of the Rocker image helps promote both testing of these choices and 
contributions, further tweaking the configuration from many members of the R community.

@@

The `debian:testing`-based stack currently includes seven images
actively maintained by the Rocker development team (Table 1).
`r-base` builds on `debian:testing`, and the other six in the stack
each build directly from `r-base`.  The `r-base` image is unique in
that it is designated as the official image for the R language by the
Docker organization itself.  This official image is reviewed and then
built by employees of Docker Inc. based on a Dockerfile maintained by
the Rocker team.  Consequently, users should refer to this image in
Docker commands without an organization namespace, _e.g._, `docker run -ti r-base` 
to access the official image.  All other images in the Rocker
project are not individually reviewed and built by Docker Inc. and must
be referenced using the `rocker` namespace,
_e.g._, `docker run -ti rocker/r-devel`.

>>>>

### Community optimized

Having a shared, transparent computational environment created by a publicly hosted, reproducible
recipe facilitates community input into configuration details. R and many of its packages
and related software can be configured with a wide range of options, compilers, different
linear-algebra libraries and so forth.  While this flexibility reflects varying needs,
many users rely on default settings which are most often are optimized more for 
simplicity of installation rather than than performance.
The Rocker recipes reflect significant community input on these choices.
This helps create a more finely tuned, optimized reference
implementation of the R environment as well as a platform for comparing and discussing these 
concerns which are often overlooked elsewhere.  Issues and Pull Requests on the Rocker 
repositories on GitHub attest to some of these discussions and improvements.
In particular, input from the Docker Inc.\ employees through the official approval process
for the `r-base` image, expertise from the Debian R maintainer and other Debian developers,
and both direct and indirect feedback from the experience and user-generated documentation
from many early adopters in the R community has helped shape and strengthen the project
over the past few years.
Widespread use of the Rocker image helps promote both testing of these choices and 
contributions, further tweaking the configuration from many members of the R community.

@@

The `debian:testing`-based stack currently includes seven images
actively maintained by the Rocker development team (Table 1).
`r-base` builds on `debian:testing`, and the other six in the stack
each build directly from `r-base`.  The `r-base` image is unique in
that it is designated as the official image for the R language by the
Docker organization itself.  This official image is reviewed and then
built by employees of Docker Inc.\ based on a Dockerfile maintained by
the Rocker team.  Consequently, users should refer to this image in
Docker commands without an organization namespace, _e.g._, `docker run -ti r-base` 
to access the official image.  All other images in the Rocker
project are not individually reviewed and built by Docker Inc.\ and must
be referenced using the `rocker` namespace,
_e.g._, `docker run -ti rocker/r-devel`.

### 2017-11-24 boettiger-eddelbuettel.tex
three small changes based on proofreading-checklist

\subsubsection{Community Optimized}\label{community-optimized}

Having a shared, transparent computational environment created by a
publicly hosted, reproducible recipe facilitates community input into
configuration details. R and many of its packages and related software
can be configured with a wide range of options, compilers, different
linear-algebra libraries and so forth. While this flexibility reflects
varying needs, many users rely on default settings which are most often
are optimized more for simplicity of installation rather than than
performance. The Rocker recipes reflect significant community input on
these choices. This helps create a more finely tuned, optimized
reference implementation of the R environment as well as a platform for
comparing and discussing these concerns which are often overlooked
elsewhere. Issues and Pull Requests on the Rocker repositories on GitHub
attest to some of these discussions and improvements. In particular,
input from the Docker Inc employees through the official approval
process for the \texttt{r-base} image, expertise from the Debian R
maintainer and other Debian developers, and both direct and indirect
feedback from the experience and user-generated documentation from many
early adopters in the R community has helped shape and strengthen the
project over the past few years. Widespread use of the Rocker image
helps promote both testing of these choices and contributions, further
tweaking the configuration from many members of the R community.

@@

The \texttt{debian:testing}-based stack currently includes seven images
actively maintained by the Rocker development team (Table 1).
\texttt{r-base} builds on \texttt{debian:testing}, and the other six in
the stack each build directly from \texttt{r-base}. The \texttt{r-base}
image is unique in that it is designated as the official image for the R
language by the Docker organization itself. This official image is
reviewed and then built by employees of Docker Inc. based on a
Dockerfile maintained by the Rocker team. Consequently, users should
refer to this image in Docker commands without an organization
namespace, \emph{e.g.}, \texttt{docker\ run\ -ti\ r-base} to access the
official image. All other images in the Rocker project are not
individually reviewed and built by Docker Inc. and must be referenced
using the \texttt{rocker} namespace, \emph{e.g.},
\texttt{docker\ run\ -ti\ rocker/r-devel}.

>>>>

\subsubsection{Community optimized}\label{community-optimized}

Having a shared, transparent computational environment created by a
publicly hosted, reproducible recipe facilitates community input into
configuration details. R and many of its packages and related software
can be configured with a wide range of options, compilers, different
linear-algebra libraries and so forth. While this flexibility reflects
varying needs, many users rely on default settings which are most often
are optimized more for simplicity of installation rather than than
performance. The Rocker recipes reflect significant community input on
these choices. This helps create a more finely tuned, optimized
reference implementation of the R environment as well as a platform for
comparing and discussing these concerns which are often overlooked
elsewhere. Issues and Pull Requests on the Rocker repositories on GitHub
attest to some of these discussions and improvements. In particular,
input from the Docker Inc.~employees through the official approval
process for the \texttt{r-base} image, expertise from the Debian R
maintainer and other Debian developers, and both direct and indirect
feedback from the experience and user-generated documentation from many
early adopters in the R community has helped shape and strengthen the
project over the past few years. Widespread use of the Rocker image
helps promote both testing of these choices and contributions, further
tweaking the configuration from many members of the R community.

@@

The \texttt{debian:testing}-based stack currently includes seven images
actively maintained by the Rocker development team (Table 1).
\texttt{r-base} builds on \texttt{debian:testing}, and the other six in
the stack each build directly from \texttt{r-base}. The \texttt{r-base}
image is unique in that it is designated as the official image for the R
language by the Docker organization itself. This official image is
reviewed and then built by employees of Docker Inc.~based on a
Dockerfile maintained by the Rocker team. Consequently, users should
refer to this image in Docker commands without an organization
namespace, \emph{e.g.}, \texttt{docker\ run\ -ti\ r-base} to access the
official image. All other images in the Rocker project are not
individually reviewed and built by Docker Inc.~and must be referenced
using the \texttt{rocker} namespace, \emph{e.g.},
\texttt{docker\ run\ -ti\ rocker/r-devel}.
